%-------------------------
% Resume in LateX
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{4.08003pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
  \textbf{\Large \scshape Alejandro Alonso Garcia} \\ \vspace{1pt}
  \small 305-720-3963 $\bullet$ \href{mailto:alejandro.alonsog@icloud.com}{\underline{alejandro.alonsog@icloud.com}} $\bullet$ 
  \href{https://www.linkedin.com/in/alexalonso04/}{\underline{linkedin.com/in/alexalonso04}} $\bullet$
  \href{https://github.com/Alexalonso04}{\underline{github.com/alexalonso04}}
\end{center}
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   % \textbf{\href{https://sourabhbajaj.com/}
%   \textbf{{\Large Alejandro Alonso}} & Email: \href{mailto:alejandro.alonsog@icloud.com}{alejandro.alonsog@icloud.com}\\
%   % \href{https://sourabhbajaj.com/}{sourabhbajaj.com} 
%   & Mobile: \href{tel:+13057203963}{+1-305-720-3963} \\
% \end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {Master of Science in Computer Science (Machine Learning Specialization)}{Jan 2021 -- Present}
    \resumeSubheading
      {University of Florida}{Gainesville, Florida}
      {Bachelor of Science in Computer Science, Minor in Digital Arts and Sciences}{Dec 2016 -- Dec 2020}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Site Reliability Engineer II}{Sunrise, Fl}
      {American Express}{Jan 2022 -- Present}
      \resumeItemListStart
        \resumeItem{Intuitive Servicing Portal: Performance tuning efforts.Contributed to the design of dashboards to enhance visibility of the application. Design of our alerting system to also improve SLA. Performed code analysis to determine strategy to insert monitoring.}
        \resumeItem{Global Servicing Portal:Uplifted the entire platform to support performance enhancements. Created automation to deploy changes quickly and effectively. Simplified installation of new software in it.Created automation for support teams to use during major events to speed up mean time to restoration}
        \resumeItem{Summer Internship Served as technical mentor for two consecutive years for summer interns. Designed our team's summer internship program consisting of various projects such as incident categorization using machine learning and observably enhancements for our production applications}
      \resumeItemListEnd
    \resumeSubheading
      {Site Reliability Engineer III}{Sunrise, Fl}
      {American Express}{Jan 2021 -- September}
      \resumeItemListStart
        \resumeItem{Provide support for Tier 0, highly-available servicing applications, with tens of thousands of daily users.}
        \resumeItem{Created automation with Ansible to manage change management for infrastructure with more than 100 servers. This represented a reduction of more than 70\% in time and engineers required to deploy infrastructure configuration changes.}
        \resumeItem{Leveraged the Ansible framework to create server restart automation that reduced time taken to restart by 65\%, from 15 minutes per server, to 5 minutes. It also reduced the amount of engineers required to quickly orchestrate a zone restart; from 3 engineers, to just 1}
        \resumeItem{Developed a fully-modular self-healing framework using Ansible for our legacy applications running Java Virtual Machines in IBM's Websphere server. This framework reduced the amount of engineers required to support an application from 10 engineers, down to 4, incurring in significant monetary savings and better resource allocation}
        \resumeItem{Lead an automation team of 4 engineers charged with maintaining our automation development, including version control, management of our portal, on-boarding resources, documentation, and more.}
      \resumeItemListEnd
    \resumeSubheading
      {Software Engineer Intern}{Sunrise, Fl}
      {American Express}{July 2020 -- August 2020}
      \resumeItemListStart
        \resumeItem{Developed the Flask backed for an internal web application that allowed teams to report planned outages. This application saved dozens of hours yearly in unnecessary bridges and impacts from planned outages.}
        \resumeItem{Created a Python-based automation that sent change management email reports on Requests For Change (RFCs) that were close to breaching their SLA time (Service Level Agreement). This report helped improve my organization's change management metrics by 10\% by ensuring timely notifications to leadership and by reminding engineers to close RFCs on time.}
        % \resumeItem{}
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
   % \resumeSubSubheading
   %  {Software Engineer I}{Oct 2014 -- Sep 2016}
   %  \resumeItemListStart
   %     \resumeItem{Apache Beam}
   %       {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
   %  \resumeItemListEnd
 
%-------------------------------------------
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Project}
      {Details}
  \resumeSubHeadingListEnd

%
% --------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages: }{Python, Javascript, Java, C\#}
     \hfill
     \textbf{Technologies: }{React, Docker, Flask, Ansible}
   }
 \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
